---
title: "Data607_Assigment1"
author: "Fayliette Lewis"
date: "8/29/2021"
output: html_document
---

```{r, message=FALSE}
library(tidyverse)
```

## The article used is "How Baby Boomers Get High"
Link: https://fivethirtyeight.com/features/how-baby-boomers-get-high/

This article and dataset analyzes a survey that was taken in 2012 on drug use from the federal Substance Abuse and Mental Health Data Archive (SAMHDA) to see what drugs baby boomers are taking. It compares their pattern of use to other age groups. As well as how similar baby boomers are when it comes to drug use.
 
```{r }

# import datset from GitHub
url <- "https://raw.githubusercontent.com/Fayliette/MSDS_Data607/main/drug-use-by-age.csv"

# Load data set 
df <- read.csv(url, stringsAsFactors = FALSE)

# Display the first 3 rows of the data set
head(df, 3)

```
## Subset of the original data
This subset excludes the drug use frequency for each age group.

```{r}

# create a subset excluding the use frequency columns
new_df <- select(df, -contains("frequency"))
# Display the first 3 rows of the subset
head(new_df, 3)

```

## Average use
Which drug has the highest usage average?

```{r}
# create a subset with only the drug use columns
drug_use <- subset(new_df[, 3:15])
head(drug_use, 3)
# calculate mean for each column of drug use
avg_use <- sort(colMeans(drug_use), decreasing = TRUE)
avg_use
ggplot(data.frame(Mean= avg_use, Drugs = names(avg_use))) +
     geom_col(aes(Mean, Drugs))

```


As seen in the graph above, Alcohol is the drugs individuals use the most.