---
title: "FLewis_Data607_HW2"
author: "Fayliette Lewis"
date: "9/9/2021"
output: html_document
---


#### MySQL popular_movie_ratings database


```{r}
library(RMariaDB)
```

Create a variable to hold the SQL database password.

```{r}

db_password <- "FLdata607"

```

Connect to the database

```{r}

moviesDb <- dbConnect(RMariaDB::MariaDB(), 
                      user='popular_movie_ratings', 
                      password=db_password, 
                      dbname='popular_movies', 
                      host='localhost')

```

List the names of the tables in the database.
```{r}

dbListTables(moviesDb)

```

Create a query to show the *audience* table.
```{r}

audience_table <- dbSendQuery(moviesDb, "SELECT * FROM audience")
dbFetch(audience_table)
dbClearResult(audience_table)

```

Create a query to show the *movies* table.
```{r}

movie_table <- dbSendQuery(moviesDb, "SELECT * FROM movies")
dbFetch(movie_table)
dbClearResult(movie_table)

```

Create a query to show the *movie_ratings table*.
```{r}

ratings <- dbSendQuery(moviesDb, "SELECT * FROM movie_ratings")
dbFetch(ratings)
dbClearResult(ratings)

```

Which movie has the most views?
```{r}

views <- dbSendQuery(moviesDb, "SELECT m.movie_id, 
          m.movie_name, 
          m.MPAA_rating, 
          COUNT(mr.rating) AS num_views
          FROM movies m
          JOIN movie_ratings mr USING (movie_id)
          WHERE rating IS NOT NULL
          GROUP BY m.movie_id, m.movie_name, m.MPAA_rating
          ORDER BY m.movie_name")
dbFetch(views )
dbClearResult(views)

```

Which movies have ratings >= 4?
```{r}

ratings4_5 <- dbSendQuery(moviesDb, "SELECT movie_id, 
              movie_name,
              MPAA_rating, 
              rating, 
              COUNT(rating) AS number_of_ratings
              FROM movies
              JOIN movie_ratings USING(movie_id)
              WHERE rating >= 4
              GROUP BY movie_id, movie_name, MPAA_rating, rating
              ORDER BY movie_id")
dbFetch(ratings4_5)
dbClearResult(ratings4_5)

```

How many of the six movies did each person watch?
```{r}

movies_watched <- dbSendQuery(moviesDb, "SELECT a.first_name, 
                  a.last_name, COUNT(mr.rating) AS num_movies_watched
                  FROM audience a
                  JOIN movie_ratings mr USING (audience_id)
                  WHERE mr.rating IS NOT NULL 
                  GROUP BY a.first_name, a.last_name
                  ORDER BY num_movies_watched DESC")
dbFetch(movies_watched )
dbClearResult(movies_watched )

```










